Hypertension and microbiome

### 2018-12-31 lactobacillus.Rmd
Emacs
V2 mod start

```{r libraries}

library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)

```{r data}

pseq <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")

```{r}
summarize_phyloseq(pseq_filtered)
ntaxa(pseq_filtered)
pseq_filtered %>% taxa() %>% sort
phfg.pseq.rel %>% rank_names()
subset_taxa(pseq_filtered, Genus == "Lac")
taxa_unique(phfg.pseq.rel, "Phylum")
abundances(phfg.pseq.rel)

@@

taxa <- names(subset_taxa(pseq.s, Genus=="Lactobacillus"))

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
```

```{r clear session}
remove(list = ls())
```

```{R data}
pseq.genus <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
pseq.species <- readRDS("data/phfinrisk_species_ok_drop50k_2018-11-16.RDs")
```

```{r}
summarize_phyloseq(pseq)
ntaxa(pseq)
pseq %>% taxa() %>% sort
phfg.pseq.rel %>% rank_names()
subset_taxa(pseq.species, Genus == "Lactobacillus")
taxa_unique(phfg.pseq.rel, "Phylum")
abundances(phfg.pseq.rel)

@@

taxa <- subset_taxa(pseq.species, Genus=="Lactobacillus") %>% taxa()
taxa
taxa %>% kable

### 2018-12-31 rrbiome.Rmd
V2 mod start

```{r functions, include = FALSE}
print.dset <- function(dset) {
    dset %>%
        gather(Covariate, Value) %>%
        group_by(Covariate) %>%
        summarise_all(., .funs = funs(mean(as.numeric(.), na.rm = TRUE),
                                         median(as.numeric(.), na.rm = TRUE),
                                         sd(as.numeric(.), na.rm = TRUE),
                                         min(as.numeric(.), na.rm = TRUE),
                                         max(as.numeric(.), na.rm = TRUE),
                                         NAs = sum(is.na(.)),
                                         n = n(),
                                         n_distinct)) %>%
            mutate_if(is.numeric, round, 2) %>%
            kable
}

@@

```{r data}
pseq <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
```

>>>>

```{r functions, include = FALSE}
print.dset <- function(dset) {
    dset %>%
        gather(Covariate, Value) %>%
        group_by(Covariate) %>%
        summarise_all(., .funs = funs(mean(as.numeric(.), na.rm = TRUE),
                                         median(as.numeric(.), na.rm = TRUE),
                                         sd(as.numeric(.), na.rm = TRUE),
                                         min(as.numeric(.), na.rm = TRUE),
                                         max(as.numeric(.), na.rm = TRUE),
                                         NAs = sum(is.na(.)),
                                         n = n(),
                                         n_distinct)) %>%
            mutate_if(is.numeric, round, 2) %>%
            kable
}
```

@@

```{r data}
pseq.genus <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
pseq.species <- readRDS("data/phfinrisk_species_ok_drop50k_2018-11-16.RDs")
```
